The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis

### 2023-03-15 carbon_paper/tex/main.tex
paper updates

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
% \usepackage{amssymb}	% Extra maths symbols
\graphicspath{{../figures/}}

@@

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}

\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
% \newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\VICE}{\texttt{VICE}}

@@

Asymptotic Giant Branch (AGB) stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)

CCSNe are also important (.... SN reminant measurments)

@@

In Figure \ref{fig:sum} we present a sample of APOGEE subgiants. These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}. Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).

\begin{figure*}
    \centering
    \includegraphics[]{subgiants_mgh.pdf}
    \includegraphics[]{subgiants_mgfe.pdf}
    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
    \label{fig:sum}
\end{figure*}
\section{Nucleosynthesis}

Galactic chemical evolution are fundamentally intertwined with our understanding of stellar nucleosynthesis. In this paper, we are concerned with three major nucleosynthetic pathways: AGB stars, CCSNe, and Supernovae type Ia. While only AGB stars and CCSNe are producers of carbon, SNeIa Fe can be used to compare with the AGB delayed carbon component.

@@

In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
\begin{itemize}
    \item \citetalias{cristallo+11}
    \item \cristallo
    \item \cite[C11][Hi]{cristallo+11}: \citet{cristallo+11}
    \item K10: \citet{karakas10}
    \item V13: \citet{ventura+13}
    \item K16: \citet{KL16}
\end{itemize}
Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.

Figure \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider. Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.

@@

We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares
represent \citep{NKT13}, etc. etc.
\citep{LC18}
\citep{sukhbold+16}
\citep{WW95}

@@

To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for
Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in
\citet{james+22}. 
As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.

@@

We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
\begin{equation}
    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
\end{equation}

@@

\subsection{Yield Parameterization}
  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks. We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below). Our expression is:
    \begin{equation}
   y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta y_\text{O}^\text{CC} + y_\text{C, 0}^\text{CC}
    \end{equation}
   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{equilibrium} ). Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$

@@

We use data from APOGEE DR17 processed with APOSCAP. Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.

To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$ which selects stars at the base of the red giant turnoff (FIGURE and \cite{jack_subgiant})

@@

See Appendix \ref{sec:jack} for further discussion of our sample and comparison to FIORENZO.

@@

We plot time evolution tracks in Figure \ref{fig:c_evo} for $[C/\alpha]-[\alpha/H]$ and $[C/\alpha]-[Fe/H]$ for our fiducial model. Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.

@@

This is even more evident in the lower part of Figure \ref{fig:c_evo}, where we instead plot snapshots of the galactic radial trend at different times for our model. While the [C/$\alpha$]-[$\alpha$/H] trend reaches almost equilibrium at 5Gyr, the [C/$\alpha$]-[$\alpha$/Fe] trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks-9.pdf}
\includegraphics{evo_slices-2.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase [C/O]-[O/H] and [C/O]-[O/Fe] trend at 5 different time slices. 
}
\end{figure*}

\subsection{Effects of AGB Yields}
\begin{figure*}
\includegraphics[scale=0.6]{oob_agb-1.pdf}

\caption{Abundance tracks for 4 different choices of AGB models. Each panel has different abundance ratios on the axis but is otherwise the same. The black points are Jack Roberts selection of APOGEE subgiants. Each model is plotted as a line representing the mean stellar abundance in each bin on x.}
\label{fig:stars_abundances}
\end{figure*}

How much does the choice of AGB model affect chemical evolution? 
Short description of effects of AGB model choices, and how we can rule out models like V21.  Maybe point to appendex B?

@@

\begin{equation}
    \alpha_{AGB} = f_{agb} \frac{y_{desired}}{y_0^{agb}}
\end{equation}
\begin{equation}
    \alpha_{CC} = (1 - f_{agb}) \frac{y_{desired}}{y_0^{cc}}
\end{equation}

We do run models with an alternate "lateburst" stars formation history.

% \begin{figure*}
% \includegraphics[width=1.5\columnwidth]{cooh_lateburst.pdf}
% \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
% \end{figure*}

\begin{figure*}
\includegraphics[scale=0.6]{beta-1.pdf}
\includegraphics[scale=0.6]{f_agb-1.pdf}

\caption{Similar to \ref{fig:stars_abundances} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence. The bottom plot is the same except shows varying AGB fractions.}
\end{figure*}

\caption{Same as Figure \ref{fig:stars_abundances} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
\end{figure*}

\subsection{Adjusted CCSNe Yields}

\begin{figure}
    \includegraphics[scale=0.6]{cooh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure}

\begin{figure*}
\centering
\includegraphics[]{summary-2.pdf}
\caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
\label{fig:gas_phase}
\end{figure*}
\subsection{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

These models are indistinguishable in the [C/O]-[O/H] plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight. In the next section, we develop the analytic tools to explore this problem in more depth.

\subsection{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

We have found that the [C/O]-[O/Fe] relationship may provide insight into this issue. [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution. So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution. 
The metallicity-dependence of carbon yields complicates this picture because younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr, so metal-poor young stars will naturally have lower [C/O], agreeing with the slope observed in [C/O]-[O/Fe]. However, a pure CCSNe carbon model cannot reproduce the slope accurately as

\subsection{Comparison to HII Region Observations}
In Figure \ref{fig:gas_phase}, we plot our two favorite models against HII-region measured carbon abundances from **********

@@

@@

\section{The Equilibrium Approximation}\label{equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

@@

Rewriting in terms of the observed abundance ratio and dividing by $y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the carbon AGB yield, and the [C/O]-[O/H] mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
\begin{equation}
    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
\end{equation}

@@

\section{Modeling extragalactic carbon trends}
Can we use our yield estimations and apply them to extragalactic sources successfully?

@@

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

@@

We compare both of **** in Figure \ref{fig:fiorenzo_jack}.

@@

Because the predictions of the AGB yield models we consider are dwarfed by the required CCSNe carbon production to match observations (see Figure ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.

@@

\caption{Same as \ref{fig:stars_abundances} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model. A plot of the stars of our favored CCSNe model colored by radius. The contours represent the density of V+21 data. The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE. }
\end{figure*}

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{abbrevs}
% \usepackage{amssymb}	% Extra maths symbols
\graphicspath{{../figures/}}

@@

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}
\defcitealias{karakas10}{K10}
\defcitealias{KL16}{KL16}
\defcitealias{karakas+18}{K18}

\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
\newcommand{\karakas}{\citetalias{karakas10}}
\newcommand{\kl}{\citetalias{KL16}+\citetalias{karakas+18}}
\newcommand{\ventura}{\citetalias{ventura+13}}

\newabbrev\CC{Core Collapse Supernovae (CCSNe)}[CCSNe]

\newcommand{\VICE}{\texttt{VICE}}
\newcommand{\caah}{[C/Mg]-[Mg/H]}
\newcommand{\caafe}{[C/Mg]-[Mg/Fe]}

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}

@@

AGB stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)

\CC are also important (.... SN reminant measurments)

@@

In Fig. \ref{fig:subgiants} we present a sample of APOGEE subgiants. These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}. Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).

\begin{figure*}
    \centering
    \includegraphics[]{subgiants_mgh.pdf}
    \includegraphics[]{subgiants_mgfe.pdf}
    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
    \label{fig:subgiants}
\end{figure*}
\section{Nucleosynthesis}

Galactic chemical evolution are fundamentally intertwined with our
understanding of stellar nucleosynthesis. In this paper, we are concerned with
three major nucleosynthetic pathways: AGB stars, \CC, and Supernovae type Ia.
While only AGB stars and \CC are producers of carbon, SNeIa Fe can be used to
compare with the AGB delayed carbon component.

@@

In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
\begin{itemize}
    \item \citet{cristallo+11} and \citet{cristallo+15} (\cristallo).
    \item \citet{karakas10} (\karakas)
    \item \citet{ventura+13} \ventura
    \item \citet{KL16} \citet{karakas+18} \kl
\end{itemize}
Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.

Fig. \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider. Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.

@@

We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. Pink squares
represent \citep{NKT13}, etc. etc.
\citep{LC18}
\citep{sukhbold+16}
\citep{WW95}

@@

To simulate the chemical evolution of a Milky-Way-like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in \citet{james+22}.  As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.

@@

We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
\begin{equation}\label{eq:lateburst}
    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
\end{equation}

@@

\subsection{Model Stellar Yields}
We define a parameterization of a \CC~yield
  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks. We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below). Our expression is:
  \begin{equation}\label{eq:y_yields}
   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
    \end{equation}
   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ). Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$

@@

We use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP. Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.

To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$
which selects stars at the base of the red giant turnoff (FIGURE and
\cite{jack_subgiant}). We describe our selection criteria along with a 
comparison to \citet{fiorenzo+21} in Appendix \ref{sec:jack}.

@@

While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
binned data to our models as black points with dashes representing the 1-sigma
spread, as in e.g. Fig. \ref{fig:agb_sims}.

@@

We plot time evolution tracks in Fig. \ref{fig:c_evo} for \caah and \caafe for our fiducial model. Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.

@@

This is even more evident in the lower part of Fig. \ref{fig:c_evo}, where we
instead plot snapshots of the galactic radial trend at different times for our
model. While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks-9.pdf}
\includegraphics{evo_slices-2.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our
    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
}
\end{figure*}

\subsection{Effects of AGB Yields}

\begin{figure*}
\includegraphics[scale=0.6]{oob_agb-1.pdf}

\caption{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
plotted as black points with 1-std errors marked by horizontal grey dashes.
Right: same as left but for \caafe. While each AGB yield model may
differ in detail, there is minimal effect on the overall [C/Mg] trends. }
\label{fig:agb_sims}
\end{figure*}

What happens as we change our choice of AGB stellar yields? We consider four models
using the published yields in \cristallo, \karakas, \kl, and \ventura~in Fig.
\ref{fig:agb_sims}.

As we chose to leave $Y_{\rm C}^{\rm CC}$ in a functional form, we chose to
leave the total IMF-averaged carbon yield to be constant. The magnitude of
$Y_{\rm C}^{\rm CC}$
\begin{equation}
    Y_{\rm C}^{0}  = 0.005  =  Y_{\rm C}^{\rm cc} + Y_{\rm C}^{\rm agb}
\Big \rvert_{Z=Z_\odot}
\end{equation}
where we are choosing to evaluate the total IMF \CC and AGB yields at solar
metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
Table \ref{tab:alpha_agb}.

This choice of total carbon yield with our fixed choice of oxygen gives an
equilibrium value of $Z_{\rm C}/Z_{\rm O} = Y_{\rm C}/Y_{\rm O} = 0.333$ which
is reasonably consistant with the value in \citet{asplund+09} of $Z_{\rm
C}/Z_{\rm O}=0.413$ and was chosen as to match the median value of our sample
at $Z=Z_{\sun }$.

As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
each of these models is dominated by \CC production of carbon. As a result,
while the metallicity dependence of the \caah may vary, the
\caafe diagnostic shows how this small AGB fraction makes the details of
the AGB model and delay-time-distribution unchange the galaxy production of
carbon.

Appendix \ref{sec:alt_agb} describes the effects of increasing the AGB model on
resulting abundance trends. However, we use the \cristallo AGB yields for the
rest of the main discussion.

@@

\begin{equation}
    \alpha_{\rm agb} = f_{\rm agb} \frac{\Yct}{\Ycagb}
\end{equation}
\begin{equation}
    \alpha_{\rm CC} = (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}
\end{equation}

\subsection{Metallicity dependence and the AGB Fraction}
The next question is how does changing the CCSNe carbon yield affect the model?
We now consider variations of our fiducial model:
\begin{itemize}
    \item $f_{\rm agb} = 0.2$
    \item AGB model: \cristallo
    \item $Z_{\rm C}^{\rm cc} = 0.004 (Z/Z_{\sun })^{0.4}$ ($\beta = 4$)
\end{itemize}

We could chose to vary the value of $\alpha$; however, the overall scaling of
yields is unknown so our constraint is really that $Y_{\rm C}/Y_{\rm O} =
0.dfsjkhld$, based on binning from our data. As discussed in the previous
section, we chose to leave the total value of the IMF integrated yield fixed,
and then assert the AGB fraction (next section) and scale the AGB yields from
literature appropriety. As such,

As we display in Fig. \ref{fig:beta_f}, we observe that changes in $\beta$ are
approprietly reflected in the resulting \caah~trend. As the metallicity
dependence steepens with higher $\beta$, the [C/Mg] ratio becomes
correspondingly more dependent on [Mg/H].

Wow! Equilibrium!! See section \ref{sec:equilibrium}

Importantly, the \caafe trend is mostly unaffected by choosing a different
CCSNe yield. As all CCSNe enrichment happens at the same, rapid timescale, by
taking a slice in [Mg/H], this metallicity dependence is effectively ignored as
the only effect can be a vertical offset if the slice is narrow enough.

So, the scaling of the trend and metallicity dependence of carbon (as seen in
the \caah~trend) gives information on the total carbon yield and the behavior
of CCSNe (as the dominating producer of carbon);
the \caafe trend exposes the delayed effect of carbon from AGB contribution.

\subsection{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight. In the next section, we develop the analytic tools to explore this problem in more depth.

We consider a simple modification of our SFH described by our lateburst model
(see Equation \ref{eq:lateburst})

\begin{figure*}\label{fig:beta_f}
\includegraphics[scale=0.6]{beta-1.pdf}
\includegraphics[scale=0.6]{f_agb-1.pdf}

\caption{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence. The bottom plot is the same except shows varying AGB fractions.}
\end{figure*}

\caption{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
\end{figure*}

\begin{figure}
    \includegraphics[scale=0.6]{cooh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure}

\begin{figure*}
\centering
\includegraphics[]{summary-2.pdf}
\caption{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
\label{fig:gas_phase}
\end{figure*}
\subsection{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

We have found that the \caah~relationship may provide insight into this issue. [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution. So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution. 
The metallicity-dependence of carbon yields complicates this picture because
younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr,
so metal-poor young stars will naturally have lower [C/O], agreeing with the
slope observed in\caafe. However, a pure CCSNe carbon model cannot reproduce the slope accurately as

\subsection{Comparison to Observations}

Beyond Milky Way stars, astronomers have observed carbon to oxygen ratios in
HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
us to probe gas-phase abundances of carbon in our galaxy and other types of
galaxies from dwarf to elliptical.

In Fig. \ref{fig:gas_phase}, we plot our fiducial model's gas phase abundances
at present day and 2Gyr compared to C/O
abundances measured in both stars, our subgiant sample, halo stars, galaxies,
and even Damped Lynman Alpha (DLA) systems.

@@

Measuring carbon in the gas phase is challenging. Carbon emission lines are
very weak compared to other common lines, (visible/etc.).
Temperature/modelining limitations. Lack of strong HII calibration.

@@

Our model fails to capture the trend past [$\alpha$/H]$=-1$. As our knowledge
of stellar evolution is limited, our knowledge of extremely metal poor stellar
evolution is extremely limited. (despite a pure H/He born star appearing
simpler lolol). A variety of explanation for the increasing relative carbon
enrichments for metal-poor stars have been proposed (e.g. ...). The likely case
that Population III star supernovae produced high abundances of carbon seems
most plausable, especially given our uncertainty in the carbon yields and the
short timescales required to create this enhancement (e.g. $z\sim 2$ DLA,
dwarfs, etc.) make it unlikely that AGB stars could be the culprit.

As any constraints in this regieme are poor, we choose to only qualitatively
conclude that CCSNe carbon production increases at extremely low metallicity
but the details of this remains an open question.

Can we use our yield estimations and apply them to extragalactic sources successfully?

\section{The Equilibrium Approximation}\label{sec:equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

@@

Rewriting in terms of the observed abundance ratio and dividing by
$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
\begin{equation}
    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
\end{equation}

@@

@@

Directions-->SneIa/AGB trends as a constraint on DTD.
Observations of Carbon in metal poor stars, extragalactic (call out any
existing surveys in e.g. APOGEE/DESI?)
Abundance ratios (e.g.C12/C13) as additional constraints

@@

We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.

@@

Because the predictions of the AGB yield models we consider are dwarfed by the
required CCSNe carbon production to match observations (see Fig. ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.

@@

\caption{Same as \ref{fig:agb_sims} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model. A plot of the stars of our favored CCSNe model colored by radius. The contours represent the density of V+21 data. The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE. }
\end{figure*}
